**Density Dependence**

### 2023-02-14 Rmd/ddMac.Rmd
ddMac.Rmd

```{r, eq}
par=teleost[c("linf","k","t0","l50","a","b"),dimnames(teleost)$iter=="Scomber scombrus"]
par=lhPar(par,m1=0.2/(300^-0.288),m2=-0.28,m3=NA)
eq =lhEql(par,m="lorenzen")
```

@@

```{r, dd-par}
par=rbind(par,
          FLPar(c(m1=0.15/(300^-0.288),m2=-0.28,
                  bref =c(refpts(eq)["msy","biomass"]),
                  delta=-0.2,
                  matk = 0.2,
                  w50  =par["a"]*par["l50"]^par["b"],
                  alpha=-0.2)))

@@

```{r}
dat=transform(dat,mat=1/(1+exp(-par["matk"]*(mass-par["w50"]))))

@@

```{r}
dat=transform(dat,m=c(par["m1"])*(mass^c(par["m2"])))

@@

  mat(     x)=1/(1+exp(-par["matk"]*(stock.wt(x)-par["w50"])))
  m(       x)=par["m1"]%*%(stock.wt(x)%^%par["m2"])
  x=brp(x)}

>>>>

```{r, eq}
par=teleost[c("linf","k","t0","l50","a","b"),dimnames(teleost)$iter=="Scomber scombrus"]
# par=lhPar(par,m1=0.2/(300^-0.288),m2=-0.28,m3=NA)
par=lhPar(par,m1=0.15/(300^-0.288),m2=-0.288,m3=NA)
eq =lhEql(par,m="lorenzen")
```

@@

```{r, dd-par}
par=rbind(par,
          FLPar(c(
                  # m1=0.15/(300^-0.288),m2=-0.28,
                  bref =c(refpts(eq)["msy","biomass"]),
                  delta=-0.2,
                  matk = 0.2,
                  w50  =par["a"]*par["l50"]^par["b"],
                  alpha=-0.2)))

@@

```{r message=FALSE, warning=FALSE}
dat=transform(dat,mat=1/(1+exp(-par["matk"]*(mass-par["w50"]))))

@@

```{r message=FALSE, warning=FALSE}
dat=transform(dat,m=c(par["m1"])*(mass^c(par["m2"])))

@@

  mat(     x)=1/(1+exp(-par["matk"]*(stock.wt(x)-par["w50"])))
  m(       x)=par["m1"]%*%(stock.wt(x)%^%par["m2"])
  x=brp(x)
}
